---
title: "Midpoint Delieverable - Learning Chinese"
author: "Language Lovers Team"
output: html_document
---

```{r echo = FALSE, message=FALSE, warning=FALSE}

# Sources
source("scripts/summary-table.R")
source("scripts/chart1.R")
source("scripts/chart2.R")
source("scripts/chart3.R")

# Load the 'knitr' library
library(dplyr)
library(htmltools)
library(knitr)

# Dataset
data <- read.csv("data/MLA_Language_Enrollment_Database.csv",
  stringsAsFactors = FALSE)
```

## Introduction

Given China's increasingly important role on the global stage, 
more and more Americans are considering learning Chinese
as a second language. As a group, we were interested in 
examining how this trend has grown over the past few decades,
and what conclusions can be drawn from its growth.

We made our conclusions based on data gathered by a series of 25 surveys
conducted by the MLA (Modern Language Association) between 1958 and 2016. 

These surveys collected detailed enrollment information on foriegn languages
from colleges across the US. The data is extensive, containing 208,020
observations and 24 features. The collection of the data was primarily
funded by the United States Department of Education, with additional funding
from several other institutions.

After reviewing the data, we had three main questions:

1) Where in the US are students studying Chinese?
2) How popular of a language is Chinese compared to other foriegn
languages currently? 
3) How does the growth of enrollment in Chinese compare to other
foreign languages? 

In the following sections, we provide charts to answer the above questions, 
as well as summarize the important points of the data in a table.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(dplyr)
source('scripts/summary.R')
```

```{r, echo=FALSE}
sum_info <- get_summary_info(data)
all_learners_total <- sum_info$all_learners_total
all_learners_total_2016 <- sum_info$all_learners_total_2016
chinese_learners_total <- sum_info$chinese_learners_total
chinese_learners_total_2016 <- sum_info$chinese_learners_total_2016
chinese_all_percentage_2016 <- sum_info$chinese_all_percentage_2016
chinese_all_percentage <- sum_info$chinese_all_percentage
cali_chinese_percent_2016 <- sum_info$cali_chinese_percent_2016
cali_chinese_percent <- sum_info$cali_chinese_percent
school_chinese_2016 <- sum_info$school_chinese_2016
school_chinese <- sum_info$school_chinese
school_chinese_unique_2016 <- sum_info$school_chinese_unique_2016
school_chinese_unique <- sum_info$school_chinese_unique_2016
```

## Summary Information

For our dataset, the dataset we used gave us informations about what second
languages different universities are teaching in certain terms, years, and the
groups of students studying these languages
(e.g. undergraduates and graduates).
There is a total of `r all_learners_total` counts of students who have been
learning a second language from 1958 to 2016 and `r all_learners_total_2016`
students in 2016.
From all years, there is a total of `r chinese_learners_total` counts of
students who learned Chinese and `r chinese_learners_total_2016` students who
enrolled in a Chinese class in 2016.

In terms of percentages, **`r chinese_all_percentage`%** of people learning a
language was learning Chinese and in 2016, the percentage is
**`r chinese_all_percentage_2016`%** .
Out of the total number of students learning Chinese,
**`r cali_chinese_percent`%** have been from California and in 2016 alone,
**`r cali_chinese_percent_2016`%** of students studied Chinese in California

The school with the most students who learned Chinese in 2016 is
**`r school_chinese_2016`** and from all terms, however, the school who had has
the most number of students learning Chinese is **`r school_chinese`**.

From the data, we can predict that some historic events, such as the gold rush,
has lead to not only the increase in Chinese immagrants, but also an increase
of the number of Chinese learners in those areas.

## Summary table
This table shows the total number of language learners in U.S. Colleges by 
states in 2016, and the number and percentages of Chinese learners. It is 
arranged by descending order of the percentage of Chinese learners to show 
the relative popularity of Chinese to language learners studying in U.S. 
Colleges.

```{r summary table, echo = F}
kable(summary_info(data), col.names = c("State", "Total Chinese Learners",
                                        "Total Language Learners",
                                        "Percent Chinese Learners"))
```


From the table, we can see Vermont has the largest percentage of Chinese 
learners, but California has the greatest number of Chinese learners. 
Therefore, we need to consider both the percentage and the actual number 
when determining the popularity of Chinese among language learners in U.S.
Colleges.

## Charts

### Map
Below includes multiple maps of the numbers of Chinese learners in higher 
institution across the United States. This chart intends to show the 
relationship between the **popularity of Chinese learning in different states**
in 2016. 

From the first graph of the full United States, we can see that **California**
has the most amount of Chinese learners, much higher than all other states.

```{r chart1, echo = F}
chart1(data)[[1]]
chart1(data)[[2]]
chart1(data)[[3]]
chart1(data)[[4]]
chart1(data)[[5]]
chart1(data)[[6]]
chart1(data)[[7]]
```


The following charts intend to show some more detailed comparison of numbers
by breaking them down into **regions** - West, Northwest, Midwest, Northeast,
South and Pacific. This intends to point out “Which states stands out the most
in each region?”. Among them, we can see how states like **WA, OH, NY, TX, HI**
stood out in each of thier regions.

### Bar Chart
This bar chart shows the **popularity of all second languages learnt** by U.S.
college 
students in 2016. Chinese Language is the seventh most popular language among 
all of them and the second most popular Asian language. However, there is 
still a big gap between the number of Chinese learners and that of the most 
popular language, Spanish, as the number of Spanish learners is more than 
800,000, but that of Chinese learners is less than 100,000. 

```{r chart2, echo = F}
bar_chart(data)
```

Among the top 8 languages, only 2 of them are Asian languages. We can conclude 
that in general, Asian languages are less attractive to U.S. students.

### Line Graph
The graphs below represent the **change in popularity of Chinese** at US
colleges over the past few decades, as well as the change in popularity
of chinese relative to other popular languages.

```{r chart3, echo = F}
chart3(data)[[1]]
chart3(data)[[2]]
```

From the above charts it is clear that while Chinese has increased in
popularity
considerably, it still lags far behind other languages. Though Chinese had
nearly 20,000 students enrolled in 1990, on the second chart this number
appears to be almost zero due to the vast difference in scale. This is likely
due, in part, to the explosive growth of Spanish as a second language. The
first graph also shows that there has been a slight drop in Chinese enrollment
over the past several years. 